Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-20 awipev-CO2.Rmd
one pointsize parameter update

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
# if (!require("plotly")) install.packages("plotly")
# library(plotly)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
knitr::opts_chunk$set(echo = TRUE)

@@

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
#d_all <
```

@@

# Add the flag location: some samples have been collected at the pier. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == as.POSIXct("2016-04-21 09:25:00") | 
                                         datetime == as.POSIXct("2016-02-10 14:00:00") | 
                                         datetime == as.POSIXct("2016-02-17 09:20:00") |
                                         datetime == as.POSIXct("2016-02-24 14:20:00") |
                                         datetime == as.POSIXct("2016-02-04 09:30:00") |
                                         datetime == as.POSIXct("2016-01-27 15:00:00") |
                                         datetime == as.POSIXct("2016-01-13 13:45:00") |
                                         datetime == as.POSIXct("2016-01-06 14:10:00") |
                                         datetime == as.POSIXct("2015-12-24 10:45:00") |
                                         datetime == as.POSIXct("2015-12-30 13:30:00") |
                                         datetime == as.POSIXct("2018-01-05 15:20:00") |
                                         datetime == as.POSIXct("2018-02-02 14:35:00") |
                                         datetime == as.POSIXct("2018-03-02 14:10:00") |
                                         datetime == as.POSIXct("2019-05-31 11:45:00"), 
                                       1, 0))
d <- d %>%
  dplyr::filter(location_flag == 0)

@@

### **Data availability**
The data at one minute frequency were tagged with the following quality flags

+ 1: good data
+ 3: failing the date and time test
+ 4: data not usable according to manufacturer
+ 7: failing the regional range test 
+ 12: failing the spike test (NAs from despike)
+ 13: failing the gradient test
+ 15: instrument not deployed or operated
+ 16: acid flush
+ 99: failing the final visual inspection

@@

s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "No data")
#colnames(z) <- c("flag", colnames(d)[-1]) # remove first col name (datetime)
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <-  ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  #discrete_scale(labels = labels) + 
  coord_flip() +
  geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  theme_bw()
p
rm(d)
```

@@

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(
    temp_fb = ifelse(
      datetime >= as.POSIXct("2017-03-22 08:00:00") &
        datetime <= as.POSIXct("2017-03-23 16:00:00"),
      NA,
      temp_fb
    ),
    temp_fb = ifelse(temp_fb > 15, NA, temp_fb)
  )
fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)

@@

<!-- at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at,TA_reg_corrected) -->
<!-- at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime) -->
<!-- dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>% -->
<!--    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>% -->
<!--   dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>% -->
<!--   dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>% -->
<!--   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% -->
<!--   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="UTC"), "HCl Changed", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="UTC"), "BCG Changed", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="UTC"), "Calibration 1", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="UTC"), "Calibration 2", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="UTC"), "TA analyser changed", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="UTC"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="UTC"), "Calibration mode - CRM", labelLoc = "bottom") %>% -->
<!--   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
<!--   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>% -->
<!--   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>% -->
<!--   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>% -->
<!--   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>% -->
<!--   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>% -->
<!--   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>% -->
<!--   dyAxis("y",valueRange = c(1600, 2650)) %>% -->
<!--   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
<!--   dyOptions( strokeWidth= 0) %>% -->
<!--   dyLegend(show = "follow")   %>% -->
<!--   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>% -->
<!--     dyRangeSelector(height = 30, dateWindow= NULL) -->

@@

```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
TAevents <- as.POSIXct(c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00",
              "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(),
              "%Y-%m-%d %H:%M:%S")))
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="TA, calculated from sal_mix (blue) and reference (red)", ylab="Total alkalinity") %>%
  #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="at_calc",color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="at (ref)",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="UTC"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="UTC"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="UTC"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="UTC"), "Calibration 2", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="UTC"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="UTC"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="UTC"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  #dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <-
  dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    "pco2_corr",
    label = "Corrected pCO2",
    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(
    "pco2_calc",
    label = "pco2_calc",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyEvent(
    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)
```

@@

# set deployment period when seaFET is in/out of water
sfinterv <- as.POSIXct(c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00"))

>>>>

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)
library(plotly)
library(htmlwidgets)
knitr::opts_chunk$set(echo = TRUE)

@@

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

# Add the flag location: some samples have been collected at the pier. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1, 0)
  )
d <- d%>%
  dplyr::filter(location_flag== 0)

@@

### **Data availability**
TO DO: add here an horizontal bar plot showing the percent availability of the data

@@

s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d, datetime >= "2017-08-29 10:00:00")
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d, datetime >= "2017-08-24 19:00:00")
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "No data")
#colnames(z) <- c("flag", colnames(d)[-1]) # remove first col name (datetime)
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <-  ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  discrete_scale(labels = labels) + 
  #coord_flip() +
  geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  theme_bw()
p
rm(d)
```

@@

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(temp_fb = ifelse(datetime >= "2017-03-22 08:00:00" & datetime <= "2017-03-23 16:00:00", NA, temp_fb),
                temp_fb = ifelse(temp_fb >15, NA, temp_fb))

@@

<!-- at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at,TA_reg_corrected) -->
<!-- at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime) -->
<!-- dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>% -->
<!--    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>% -->
<!--   dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>% -->
<!--   dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>% -->
<!--   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% -->
<!--   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>% -->
<!--   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
<!--   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>% -->
<!--   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>% -->
<!--   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>% -->
<!--   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>% -->
<!--   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>% -->
<!--   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>% -->
<!--   dyAxis("y",valueRange = c(1600, 2650)) %>% -->
<!--   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
<!--   dyOptions( strokeWidth= 0) %>% -->
<!--   dyLegend(show = "follow")   %>% -->
<!--   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>% -->
<!--     dyRangeSelector(height = 30, dateWindow= NULL) -->

@@

```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="TA, calculated from sal_mix (blue) and reference (red)", ylab="Total alkalinity") %>%
  #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="at_calc",color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="at (ref)",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  #dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <-
  dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    "pco2_corr",
    label = "Corrected pCO2",
    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(
    "pco2_calc",
    label = "pco2_calc",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyEvent(
    as.POSIXct("2016-02-28 12:00:00", tz = "GMT"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2017-02-07 12:00:00", tz = "GMT"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-04-16 12:00:00", tz = "GMT"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-10-31 15:00:00", tz = "GMT"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2019-09-03 15:00:00", tz = "GMT"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)
```

@@

# set deployment period when seaFET is in/out of water
sfinterv <- c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00")

# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01,
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02,
                                ifelse(datetime >= sfinterv[3] , 03,NA ))))
